\documentclass[a4paper, 12pt,english]{report}
                                    %romanian
%pentru limba romana
\usepackage{babel}
\usepackage[latin2]{inputenc}
%se pot comenta si elimina (la fel ca si optiunea de mai sus -english) daca textul nu contine diacritice

\usepackage{url}
\usepackage{amssymb}

\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode} 
\usepackage{multirow}

\renewcommand{\algorithmiccomment}[1]{\hfill // #1} 

\usepackage{geometry}
\usepackage{graphics}

%\usepackage{color}           %\textcolor{red}{ De completat ... }

%pentru link la citari
\usepackage[dvips]{graphicx,color}
\usepackage[colorlinks]{hyperref}

\hypersetup{
pdftitle={BachelorThesis},
pdfauthor={Norbert},
pdfkeywords={pdf, latex, tex, ps2pdf, pdflatex},
bookmarksnumbered,
pdfstartview={FitH},
urlcolor=blue,
colorlinks=true,
linkcolor=blue,
citecolor=blue,}


\geometry{a4paper,top=2.5cm,left=3cm,right=3cm,bottom=2.5cm}
%controlling the appearance of your headers and footers
\usepackage{fancyhdr}
\pagestyle{fancy}


\lhead{}
\chead{}
\renewcommand{\headrulewidth}{0.2pt}
\renewcommand{\footrulewidth}{0.2pt}



\begin{document}

\begin{titlepage}

	\begin{center}
		\Large{{BABES-BOLYAI UNIVERISTY CLUJ-NAPOCA}}
		\Large{{FACULTY OF MATHEMATICS AND COMPUTER SCIENCE}}
		
		\vspace{8cm}
		
		\textbf{BACHELOR THESIS}
		
		\vspace{1cm}
		\Huge\textbf{{Static Sign-Language Recognition using RetinaNet}}
		\fontsize{12}{14}
		
	\end{center}
	\vspace{6cm}
	
	\hspace*{0.8cm}Supervisor: \hfill  Author: \hspace*{0.8cm} \\    
	\textbf{Prof. Dr. Laura DIOSAN  \hfill  \textbf{Norbert-Cristian BERECZKI}}
	
	\vspace{2cm}
	\begin{center}
		\Large{2018}
	\end{center}
\end{titlepage}  
    
    
\newpage
\thispagestyle{empty}
\mbox{}
\newpage
\pagenumbering{roman} 

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\cleardoublepage
%\addcontentsline{toc}{Abstract}{\\  Abstract \ . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . } 
\begin{abstract}
\vspace{0.5cm}	
\hrule
\vspace{0.5cm}	
%\cleardoublepage

In the last three decates there have been significant contributions related to sign-language recognition. So it is imperative to continue contributing to this 
topic in order to improve how deaf-mute people interact with society. Many papers have been published presenting methods using either hand-colored gloves or using 
special devices such as Microsoft Kinect. In the real world, most of the time, devices like these are difficult to aquire. However, image streams and videos are 
more common means of procuring data from a user. In this work we present a real-time American-Sign-Language translator. In order to develop such a tranlator we employed 
Machine Learling techniques. Our model is based on transfer learning by using a pre-trained RetinaNet convolutional network and fine-tune using University of Massey dataset and an open source dataset found on github [6]. 
\break
\break
This work is the result of my own activity. I have neither given nor received unauthorized assistance on this work. 

\end{abstract}
\tableofcontents
           
\newpage
\renewcommand{\headrulewidth}{0.2pt}
\renewcommand{\footrulewidth}{0.2pt}
\pagenumbering{arabic}

\include{Chapters/Introduction}
\include{Chapters/Chapter2}
\include{Chapters/Chapter3}
\include{Chapters/Chapter4}
\include{Chapters/Chapter5}

\include{Chapters/Conclusions}

%ca sa apara bibliografia in contents
\clearpage
\addcontentsline{toc}{chapter}{Bibliografy}

\include{Chapters/Biblio}

\end{document}